\section{Notes}
\begin{itemize}
	\item prescaler: another downconverter in the feedback path. " For example, let’s assume that a 900 MHz output is required with
	10 kHz spacing. A 10 MHz reference frequency might be used, with the R-Divider set at
	1000. Then, the N-value in the feedback would need to be of the order of 90,000. This
	would mean at least a 17-bit counter capable of operating at an input frequency of
	900 MHz.
	To handle this range, it makes sense to precede the programmable counter with a fixed
	counter element to bring the very high input frequency down to a range at which standard
	CMOS counters will operate. This counter, called a prescaler," \cite{RF_IFCircuits}(4.56). Degrades resolution.
	\item Integer N: for high resolution, small reference is needed, but large N. Large N means Large phase noise. Low reference frequency limits PLL lock time. \cite{RF_IFCircuits} (4.59)
	\item Fractional N: "It is possible to implement division by a fraction over a long period of time by alternatey dividing by two integers(divide by 2.5 can be achieved by dividing
	successively by 2 and 3). So, how does one divide by X or (X + 1) (assuming that the
	fractional number is between these two values)? Well, the fractional part of the number
	can be allowed to accumulate at the reference frequency rate. \cite{RF_IFCircuits}(4.59). Frac N has higher spurious noise however.
	\item ADF5355 Math and equations: \cite{ADF5355}
	\item Channel Spacing: "By changing the value N, the VCO can be
	tuned across the frequency band of interest. The only constraint to the frequency output
	of the system is that the minimum frequency resolution, or minimum channel spacing, is
	equal to Fr. $$Channel Spacing=F_{VCO}/N=F_r$$(Fr=Frequency Reference) \cite{FracVsInt}
	\item Phase Noise:Multiplication by N raises the signals phase noise by $20Log(N)$ dB. \cite{FracVsInt}
	\item "The principle of fractionality is
	therefore a result of averaging, as there is no device that can divide by a fraction." \cite{FracVsInt}
	\item Fractional N can be much faster because the reference frequency is faster too. \cite{FracVsInt} PG.40
	\item Fractional N causes spurious noise because it is rapidly changing N values. N and N+1
\end{itemize}